Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-05-25 Manuscript.Rmd
directory restructuring, and deletion of unnecessary files

## Permutation analysis
# load parcels reported per study for each corpus
setwd('./metaresultsPOS')
templist <- dir()
studyList_sv <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())

>>>>

## Permutation analysis
# load parcels reported per study for each corpus
setwd('./meta_coords/metaresultsPOS')
templist <- dir()
studyList_sv <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())
